### 2018-11-07 Sections/errors_in_quantum_networks.tex
Vecs
Resized figs for 1 column

Alternate to known unitaries, the unitary operation implemented by a node/channel may deviate from that which is desired, in an unknown manner, thereby implementing a slightly different operation than that which we intended to engineer. Specifically, the effective unitary can be represented as the ideal unitary, augmented by some deviation matrix,
\begin{align}
	\hat{U}_\mathrm{effective} = \hat{U}_\mathrm{ideal} + \hat{\Delta}_\mathrm{error},
\end{align}
where the matrix elements of $\hat{\Delta}_\mathrm{error}$ are unknown, but hopefully small. Since the unknown deviation matrix needn't be constant, it will be a function of random variables, evaluated independently for each trial of the process. Furthermore, since the deviation matrix may vary from trial to trial, QPT cannot be employed to characterise it, unlike unitaries with fixed errors.

@@

\begin{figure}[!htbp]
	\includegraphics[width=0.475\textwidth]{free_space_dispersion}
	\caption{Spot-size of an optical beam grows quadratically with distance from the source. If the beam is then collected via a camera with aperture area $A'$, any component of $A$ falling outside of $A'$ is effectively lost, yielding an effective loss channel with efficiency \mbox{$\eta = \frac{A'}{A} = \frac{A'}{\pi d^2 \tan^2\theta} = O\left(\frac{1}{d^2}\right)$}.} \label{fig:free_space_disp}
\end{figure}

>>>>

Alternate to known unitaries, the unitary operation implemented by a node/channel may deviate from that which is desired, in an unknown manner, thereby implementing a slightly different operation than that which we intended to engineer. Specifically, the effective unitary can be represented as the ideal unitary, augmented by some deviation matrix,
\begin{align}
	\hat{U}_\mathrm{effective} = \hat{U}_\mathrm{ideal} + \hat{\Delta}_\mathrm{error},
\end{align}
where the matrix elements of $\hat{\Delta}_\mathrm{error}$ (which is not unitary in general) are unknown, but hopefully small. Since the unknown deviation matrix needn't be constant, it will be a function of random variables, evaluated independently for each trial of the process. Furthermore, since the deviation matrix may vary from trial to trial, QPT cannot be employed to characterise it, unlike unitaries with fixed errors.

@@

\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.475\textwidth]{free_space_dispersion}
	\caption{Spot-size of an optical beam grows quadratically with distance from the source. If the beam is then collected via a camera with aperture area $A'$, any component of $A$ falling outside of $A'$ is effectively lost, yielding an effective loss channel with efficiency \mbox{$\eta = \frac{A'}{A} = \frac{A'}{\pi d^2 \tan^2\theta} = O\left(\frac{1}{d^2}\right)$}.} \label{fig:free_space_disp}
\end{figure}

### 2018-11-07 Sections/introduction.tex
Resized figs for 1 column

\begin{itemize}
	\item Searching unstructured databases (Sec.~\ref{sec:quantum_search}):\index{Grover's algorithm}
		\begin{itemize}
		\item Grover's algorithm \cite{bib:Grover96}.
		\item Quadratic speedup.
		\end{itemize}
	\item Satisfiability \& optimisation problems\footnote{A satisfiability problem is one where we search a function's input space for a solution(s) satisfying a given output constraint. The hardest such problems, like the archetypal 3-\textsc{SAT}\index{3-SAT problem} problem, are \textbf{NP}-complete.}\index{NP \& NP-complete}\index{Optimisation}\index{Satisfiability problems} (Sec.~\ref{sec:optimising_the_world}):
		\begin{itemize}
			\item Grover's algorithm.
			\item Quadratic speedup.
			\item Includes solving \textbf{NP}-complete problems, and brute-force cracking of private encryption keys.\index{Satisfiability problems}
			\item Many optimisation problems are \textbf{NP}-complete or can be approximated in \textbf{NP}-complete.\index{Optimisation}
			\end{itemize}
	\item Period finding and integer factorisation\index{Shor's algorithm} (Sec.~\ref{sec:shors_alg}):
		\begin{itemize}
		\item Shor's algorithm \cite{bib:ShorFactor}.
		\item Exponential speedup.
		\item This compromises both Rivest, Shamir \& Adleman (RSA) and elliptic-curve public-key cryptography \cite{bib:RSA}\index{RSA encryption}\index{Elliptic-curve cryptography}\index{Public-key cryptography}, the most widely used cryptographic protocols on the internet today.
		\end{itemize}
	\item Simulation of quantum systems\index{Quantum simulation} (Sec.~\ref{sec:quantum_sim_alg}):
		\begin{itemize}
			\item Lloyd's algorithm \cite{bib:lloyd1996universal}.
			\item Exponential speedup.
			\item This includes simulation of: molecular and atomic interactions in the study of quantum chemistry or nuclear physics; interactions between drug molecules and organic molecules for drug design; genetic interactions for the study of genetics and genetic medicine; nanoscale semiconductor physics for integrated circuit design; and much more.
			\end{itemize}
	\item Simulation of quantum field theories\index{Simulating quantum field theories}:
		\begin{itemize}
		 \item Jordan-Lee-Preskill algorithm \cite{bib:JLP, bib:RohdeWavelet15}
		 \item Exponential speedup.
		 \item A key area of fundamental physics research.
		 \end{itemize}
	\item Topological data analysis (Sec.~\ref{sec:TDA}):\index{Topological data analysis}
		\begin{itemize}
		\item Lloyd's algorithm \cite{bib:lloyd2016quantum, USTCexperiment}.
		\item Exponential speedup.
		\item Broad applications including: social media network analysis\index{Social media network analysis}; consumer behaviour\index{Consumer behaviour}; behavioural dynamics\index{Behavioural dynamics}; neuroscience\index{Neuroscience}; and higher-dimensional signal and image processing\index{Signal \& image processing}.
		\end{itemize}
	\item Solving linear systems of equations (Sec.~\ref{sec:linear_systems}):\index{Linear systems}
		\begin{itemize}
		\item \comment{To do} \cite{bib:harrow2009quantum, bib:BerryLinear}.
		\item Exponential speedup.
		\item Widespread applications in linear algebra and calculus.
		\end{itemize}
	\item Quantum machine learning (Sec.~\ref{sec:quantum_mind}):\index{Quantum machine learning}
		\begin{itemize}
		\item Lloyd's algorithm \cite{bib:lloyd2013quantum}.
		\item This includes putting an end to humanity \latinquote{Ne obliviscaris.}
		\end{itemize}
\end{itemize}
An elementary technical overview of some of these archetypal algorithms is presented in Sec.~\ref{sec:quantum_algs}.

@@

The TCP layer remains largely transparent to the end-user, enabling virtual software interfaces to remote digital assets that behave as though they were local. This allows high-level services such as the File Transfer Protocol (FTP)\index{File Transfer Protocol (FTP)}, the worldwide web, video and audio streaming, and outsourced computation on supercomputers, as though everything was taking place locally, with the end-user oblivious to the underlying networking protocols, which have been abstracted away. To the user, YouTube videos or Spotify tracks behave as though they were held as local copies. And FTP or DropBox allow storage on a distant data centre to be mounted as though it were a local volume. We foresee a demand for these same criteria in the quantum era.

>>>>

\begin{itemize}
	\item Searching unstructured databases (Sec.~\ref{sec:quantum_search}):\index{Grover's algorithm}
		\begin{itemize}
		\item Grover's algorithm \cite{bib:Grover96}.
		\item Quadratic speedup.
		\end{itemize}
	\item Satisfiability \& optimisation problems\footnote{A satisfiability problem is one where we search a function's input space for a solution(s) satisfying a given output constraint. The hardest such problems, like the archetypal 3-\textsc{SAT}\index{3-SAT problem} problem, are \textbf{NP}-complete.}\index{NP \& NP-complete}\index{Optimisation}\index{Satisfiability problems} (Sec.~\ref{sec:optimising_the_world}):
		\begin{itemize}
			\item Grover's algorithm.
			\item Quadratic speedup.
			\item Includes solving \textbf{NP}-complete problems, and brute-force cracking of private encryption keys.\index{Satisfiability problems}
			\item Many optimisation problems are \textbf{NP}-complete or can be approximated in \textbf{NP}-complete.\index{Optimisation}
			\end{itemize}
	\item Period finding and integer factorisation\index{Shor's algorithm} (Sec.~\ref{sec:shors_alg}):
		\begin{itemize}
		\item Shor's algorithm \cite{bib:ShorFactor}.
		\item Exponential speedup.
		\item This compromises both Rivest, Shamir \& Adleman (RSA) and elliptic-curve public-key cryptography \cite{bib:RSA}\index{RSA encryption}\index{Elliptic-curve cryptography}\index{Public-key cryptography}, the most widely used cryptographic protocols on the internet today.
		\item This problem is believed to be \textbf{NP}-intermediate -- an \textbf{NP} problem that lies outside \textbf{P} (and is therefore classically hard), but which is not \textbf{NP}-complete (the `hardest' of the \textbf{NP} problems).
		\end{itemize}
	\item Simulation of quantum systems\index{Quantum simulation} (Sec.~\ref{sec:quantum_sim_alg}):
		\begin{itemize}
			\item Lloyd's algorithm \cite{bib:lloyd1996universal}
			\item Exponential speedup.
			\item This includes simulation of: molecular and atomic interactions in the study of quantum chemistry or nuclear physics; interactions between drug molecules and organic molecules for drug design; genetic interactions for the study of genetics and genetic medicine; nanoscale semiconductor physics for integrated circuit design; and much more.
			\end{itemize}
	\item Simulation of quantum field theories\index{Simulating quantum field theories}:
		\begin{itemize}
		 \item Jordan-Lee-Preskill algorithm \cite{bib:JLP, bib:RohdeWavelet15}
		 \item Exponential speedup.
		 \item A key area of fundamental physics research.
		 \end{itemize}
	\item Topological data analysis (Sec.~\ref{sec:TDA}):\index{Topological data analysis}
		\begin{itemize}
		\item Lloyd's algorithm \cite{bib:lloyd2016quantum, USTCexperiment}.
		\item Exponential speedup.
		\item Broad applications including: social media network analysis\index{Social media network analysis}; consumer behaviour\index{Consumer behaviour}; behavioural dynamics\index{Behavioural dynamics}; neuroscience\index{Neuroscience}; and higher-dimensional signal and image processing\index{Signal \& image processing}.
		\end{itemize}
	\item Solving linear systems of equations (Sec.~\ref{sec:linear_systems}):\index{Linear systems}
		\begin{itemize}
		\item \comment{To do} \cite{bib:harrow2009quantum, bib:BerryLinear}.
		\item Exponential speedup.
		\item Widespread applications in linear algebra and calculus.
		\end{itemize}
	\item Quantum machine learning (Sec.~\ref{sec:quantum_mind}):\index{Quantum machine learning}
		\begin{itemize}
		\item Lloyd's algorithm \cite{bib:lloyd2013quantum}.
		\item This includes putting an end to humanity \latinquote{Ne obliviscaris.}
		\end{itemize}
\end{itemize}
An elementary technical overview of some of these archetypal algorithms is presented in Sec.~\ref{sec:quantum_algs}.

@@

The TCP layer remains largely transparent to the end-user, enabling virtual software interfaces to remote digital assets that behave as though they were local. This allows high-level services such as the File Transfer Protocol (FTP)\index{File Transfer Protocol (FTP)}, the worldwide web, video and audio streaming, and outsourced computation on supercomputers, as though everything was taking place locally, with the end-user oblivious to the underlying networking protocols, which have been abstracted away. To the user, YouTube videos or Spotify tracks behave as though they were held as local copies. And FTP or DropBox allow storage on a distant data-centre to be mounted as though it were a local volume. We foresee a demand for these same criteria in the quantum era.

### 2018-11-07 Sections/network_algorithms.tex
No cloning proof
Resized figs for 1 column

The BFS algorithm is particularly applicable to pathfinding in ad hoc networks. Consider the situation where there is no central authority with full knowledge of the network, overseeing network operation. Rather, everyone needs to figure things out for themselves by only interrogating their neighbours, to whom they have direct connections. This directly leads to a BFS algorithm, where a node speaks to each of its neighbours in turn, who subsequently do the same thing, yielding a recursive algorithm. This can be naturally parallelised, as each node can be interrogating its neighbours independently, thereby implementing a distributed BFS algorithm. Note that, when searching for a target node, while the BFS algorithm obviously finds the target using the smallest number of hops (i.e a lowest-order route), it needn't necessarily find the route with the lowest cost (which is distinct from the number of hops in general). Shortest-path algorithms require a priori knowledge of the full network graph, discussed in Sec.~\ref{sec:shortest_path}.

@@

\begin{figure}[!hbtp]
\includegraphics[clip=true, width=0.35\textwidth]{vehicle_routing_alg}
	\caption{Example of the vehicle routing problem, the multi-user generalisation of the shortest-path problem, where the goal is to minimise the total cost across all users. Intuitively, because whenever individual shortest-paths intersect one must trial different prioritisations, the combinatorics of this grow exponentially with the number of competing users.}\label{fig:VRS}
\end{figure}

>>>>

The BFS algorithm is particularly applicable to pathfinding in ad hoc networks. Consider the situation where there is no central authority with full knowledge of the network, overseeing network operation. Rather, everyone needs to figure things out for themselves by only interrogating their neighbours, to whom they have direct connections. This directly leads to a BFS algorithm, where a node speaks to each of its neighbours in turn, who subsequently do the same thing, yielding a recursive algorithm. This can be naturally parallelised, as each node can be interrogating its neighbours independently, thereby implementing a distributed BFS algorithm. Note that, when searching for a target node, while the BFS algorithm obviously finds the target using the smallest number of hops (i.e a lowest-order route), it needn't necessarily find the route with the lowest cost (which is distinct from the number of hops in general). Shortest-path algorithms require \textit{a priori} knowledge of the full network graph, discussed in Sec.~\ref{sec:shortest_path}.

@@

\begin{figure}[!hbtp]
\includegraphics[clip=true, width=0.475\textwidth]{vehicle_routing_alg}
	\caption{Example of the vehicle routing problem, the multi-user generalisation of the shortest-path problem, where the goal is to minimise the total cost across all users. Intuitively, because whenever individual shortest-paths intersect one must trial different prioritisations, the combinatorics of this grow exponentially with the number of competing users.}\label{fig:VRS}
\end{figure}

### 2018-11-07 Sections/network_topologies.tex
Resized figs for 1 column

According to the Bianconi-Barab{\'a}si fitness model\index{Bianconi-Barab{\'a}si fitness model} \cite{bib:BBfitness, bib:BAfitness}, let \mbox{$\eta_i>0$} be the \textit{fitness factor}\index{Fitness factors} of node $i$, which follow a distribution $\rho(\eta)$, a characteristic of the network. Then the fitness parameters\index{Fitness parameters} are defined to be normalised such that,
\begin{align}
\Pi_i = \frac{\eta_i k_i}{\sum_j \eta_j k_j}.	
\end{align}
Upon adding a new node of degree $m$ to the network, the temporal dynamics will satisfy,
\begin{align}
\frac{\partial P(k_i)}{\partial t}= m\Pi_i.	
\end{align}
The probability distribution can then be shown to have solution,
\begin{align}
P(k) \approx \int \rho(\eta)\frac{C}{\eta}\left(\frac{m}{k}\right)^\frac{C}{\eta+1}\,d\eta,
\end{align}
where,
\begin{align}
	C &= \int \frac{\rho(\eta)\cdot\eta}{1-\beta(\eta)},\nonumber\\
	\beta(\eta) &= \frac{\eta}{C},
\end{align}
which is a linear combination of power law relationships, as required for the definition for scale-free.

Intuitively, why would we expect computer networks (classical or quantum) to be scale-free? To answer this, we simply must establish whether the preferential attachment property will hold. In computer networks there are many reasons why we might expect this to be the case:
\begin{itemize}
	\item Distance\index{Cost vector analysis}: connecting to more highly-connected nodes reduces (on average) the number of channels data packets must traverse to reach their destination, making them `cheaper' in terms of their cost vector analysis (Sec.~\ref{sec:quantum_meas_cost}).
	\item Availability\index{Availability}: larger nodes are more likely to have unused network sockets\index{Sockets} available for use by new nodes. For example, one is more likely to be able to successfully sign up for an internet connection with a major national ISP than a small, local upstart player.
	\item Economies of scale\index{Economies of scale}: the dollar cost per connection of a larger node is likely to be less than for a smaller one, owing to economies of scale. For example, the cost per FLOP of a large-scale supercomputer is far less than for a desktop PC, and Google's data-centres experience lower cost-per-bandwidth on their internet connections than home-users connecting via their ISPs.
\end{itemize}

One notable characteristic of scale-free networks is their hierarchical structure, with a small number of very highly-connected `hubs'\index{Hub nodes} at the top of the food chain, which quickly connect onto smaller hubs, and so on down the food chain with decreasing connectivity.

@@

Fig.~\ref{fig:graph_deletions} illustrates some examples of these two extreme cases.

>>>>

According to the Bianconi-Barab{\'a}si fitness model\index{Bianconi-Barab{\'a}si fitness model} \cite{bib:BBfitness, bib:BAfitness}, let \mbox{$\eta_i>0$} be the \textit{fitness factor}\index{Fitness factors} of node $i$, which follow a distribution $\rho(\eta)$, a characteristic of the network. Then the fitness parameters\index{Fitness parameters} are defined to be normalised such that,
\begin{align}
\Pi_i = \frac{\eta_i k_i}{\sum_j \eta_j k_j}.	
\end{align}
Upon adding a new node of degree $m$ to the network, the temporal dynamics will satisfy,
\begin{align}
\frac{\partial P(k_i)}{\partial t}= m\Pi_i.	
\end{align}
The probability distribution can then be shown to have solution,
\begin{align}
P(k) \approx \int \rho(\eta)\frac{C}{\eta}\left(\frac{m}{k}\right)^\frac{C}{\eta+1}\,d\eta,
\end{align}
where,
\begin{align}
	C &= \int \frac{\rho(\eta)\cdot\eta}{1-\beta(\eta)}\,d\eta,\nonumber\\
	\beta(\eta) &= \frac{\eta}{C},
\end{align}
which is a linear combination of power law relationships, as required for the definition for scale-free.

Intuitively, why would we expect computer networks (classical or quantum) to be scale-free? To answer this, we simply must establish whether the preferential attachment property will hold. In computer networks there are several reasons why we might expect this to be the case:
\begin{itemize}
	\item Distance\index{Cost vector analysis}: connecting to more highly-connected nodes reduces (on average) the number of channels data packets must traverse to reach their destination, making them `cheaper' in terms of their cost vector analysis (Sec.~\ref{sec:quantum_meas_cost}).
	\item Availability\index{Availability}: larger nodes are more likely to have unused network sockets\index{Sockets} available for use by new nodes, and they are likely to be more readily accessible. For example, one is more likely to be able to successfully sign up for an internet connection with a major national ISP than a small, local upstart player.
	\item Economies of scale\index{Economies of scale}: the dollar cost per connection of a larger node is likely to be less than for a smaller one, owing to economies of scale. For example, the cost per FLOP of a large-scale supercomputer is far less than for a desktop PC, and Google's data-centres experience lower cost-per-bandwidth on their internet connections than home-users connecting via their ISPs.
\end{itemize}

One notable characteristic of scale-free networks is their hierarchical structure, with a small number of very highly-connected `hubs'\index{Hub nodes} at the top of the food chain, which quickly connect onto smaller hubs, and so on down the food chain with decreasing connectivity, as shown in Fig.~\ref{fig:scale_free_net}.

\begin{figure}[!htbp]
\includegraphics[clip=true,width=0.4\textwidth]{scale_free_network}
\caption{Example of a scale-free network. The graph exhibits a highly hierarchical structure, with a small number of `hub' nodes that are highly connected (green, with vertex order 5), that connect downward to a larger number of less connected nodes (purple, with order vertex 1-2).}\label{fig:scale_free_net}
\end{figure}

@@

Fig.~\ref{fig:graph_deletions} illustrates some examples of the robustness of these two extreme cases to link and node failure.
